Interfering with Noninterference \iftext\thanks{\bcp{Identify applicable funding agencies here (DARPA and NSF and...?)}}\fi

### 2020-01-10 main.tex
Notes.

@@

\bcp{I'm confused here about policy vs. property -- e.g., which contours are
  requirements and which are chosen by the micropolicy.}

@@

\iftext
\begin{itemize}
\item Should we have an intermediate classification level (``internal'' or
something) and make the policy say that it's only bad for data to flow from
$\HIGH$ to $\LOW$?  This would correspond to more realistic taint policies.

\item \bcp{Should we be talking about end-to-end or single-step NI?  I guess we
  have to begin with EENI and then get to SSNI as a (stronger) refinement.}

>>>>

\bcp{
  Following is not quite right.  Better intuition:
  \begin{itemize}
  \item A (micro-){\em policy} is a function that takes a contour to
  \begin{enumerate}
  \item a private type $X$
  \item an initial value of $X$
  \item a partial step function of type $(\MACHS,X) \rightharpoonup 
  (\MACHS,X)$ that, when defined, agrees with $\stepstounderfull$ on
  machine states.
  \end{enumerate}
  That is, it takes a starting contour and produces a runtime monitor, which
  carries along some information that it uses to decide when to terminate
  execution early.
  \item A {\em property} is a function that takes a contour to a
  prefix-closed set of (finite and/or infinite) sequences of machine states.
  That is, it takes a starting contour and produces a checker that tells
  whether a given trace is OK to observe.
  \item A policy $p$ {\em guarantees} a property $P$ if, for each contour
  $\contour$, the sequence of machine states obtained by projecting the
  sequence of ..... ARGH WHAT ABOUT VARIANTS!?!
  \end{itemize}
}

@@

@@

\iftext
\begin{itemize}
\item \bcp{Should we be talking about end-to-end or single-step NI?  I guess we
  have to begin with EENI and then get to SSNI as a (stronger) refinement.}
